---
title: "group_document"
format: html
editor: visual
---

## Emma

Loading libraries

```{r}
library("tidyverse")
```

Trying to calculate very difficult calculations

```{r}
a <- 2+2

print(a)
```

```{r}
b <- "hello"

if(a == 4){print(b)}
```

## Helena

Hello my friends, can you see me?

```{r}
2*2
```

#### New analysis

Branching

```{r}
print("My first branching")
```

## Frederik

Jeg skriver også lige lidt

```{r}
print("Her laver jeg noget")
```

#### Ny header 4

Jeg skriver lige lidt mere

```{r}
3^3
```

## Casper

Det her er noget tekst.

```{r}
print("Nu printer jeg lige lidt")
```

```{r}
## Nu kommer der lidt hurtigt matematik
if (2 + 2 == 4) {
  print("minus one that is 3")
}
```

## Laura

Here is some text

```{r}
2+2-1
```

Quick maths

<<<<<<< HEAD
## New analysis
=======
### New feature

Here is some more text

```{r}
a <- 2+2
print(a)
```

## New element

This is again some text from my own branch

```{r}
sin(3.14)
```

Lets hope it works this time

<<<<<<< HEAD


## New analysis 
>>>>>>> fccb22f48d935cf6d79cfa0dc6cac881cea1a80a
=======
## New analysis
>>>>>>> 4a658effb6d635281e755a70b2b8eb5580a4e8ac

Very cool analysis I have made just now

```{r}
print("wow very cool code")
print("crazy programming")
print(2+2)
```
